\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-06-06 expanded-appendix.tex
Preparing to upload to Computer Journal

\documentclass[10pt,a4paper]{article}
\usepackage[text={6.5in,10in},centering]{geometry}    
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\usepackage{doi}
\usepackage{longtable}
\usepackage{color}
\usepackage{amsmath,amssymb}
\usepackage{fancyhdr}    
\usepackage{graphicx}
\PassOptionsToPackage{dvipdfmx}{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}

\def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
\def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}    
\input macros.tex

\makeatletter
      \renewcommand{\thefootnote}{\arabic{footnote}}
      % count the number of bibcite{name}{value} in paper.aux
      \let\oldbibcite=\bibcite
      \newcount\mainNumberOfReferences \mainNumberOfReferences=0
      \def\bibcite#1#2{\global\advance\mainNumberOfReferences by 1\oldbibcite{#1}{#2}}
      \input paper.aux 
      \let\bibcite=\oldbibcite
\makeatother

\input generated/page-lengths.tex

>>>>

% 
% This file has been expanded from LaTeX file (appendix.tex)
%   to make this straight forward LaTeX file (expanded-appendix.tex)
%     that depends on nothing (it inputs no files apart from the document class files).
%       Each required file's text was input in situ - search for % expand
% 
% (Otherwise the file appendix.tex would use BibTeX, a macro file, tables of contents, its own and the other files's .aux files, and includes various files in generated/*, etc.)
%

\makeatletter
\relax 
\providecommand\hyper@newdestlabel[2]{}
\providecommand\HyperFirstAtBeginDocument{\AtBeginDocument}
\HyperFirstAtBeginDocument{\ifx\hyper@anchor\@undefined
\global\let\oldnewlabel\newlabel
\gdef\newlabel#1#2{\newlabelxx{#1}#2}
\gdef\newlabelxx#1#2#3#4#5#6{\oldnewlabel{#1}{{#2}{#3}}}
\AtEndDocument{\ifx\hyper@anchor\@undefined
\let\newlabel\oldnewlabel
\fi}
\fi}
\global\let\hyper@last\relax 
\gdef\HyperFirstAtBeginDocument#1{#1}
\providecommand\HyField@AuxAddToFields[1]{}
\providecommand\HyField@AuxAddToCoFields[2]{}
\citation{vancouver}
\citation{hamming}
\citation{fixit}
\citation{cosmos}
\@writefile{toc}{\contentsline {section}{\numberline {8}Further issues for Software Engineering Boards (SEBs)}{38}{section.8}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {8.a}Relationships of SEBs to Ethics Boards}{38}{subsection.8.1}\protected@file@percent }
\citation{ethics-paper}
\citation{ai-ethics}
\citation{science-lancet1,science-lancet2,lancet-learning}
\citation{jvs1,jvs2,jvs3}
\citation{sommerville,knight}
\citation{cosmos}
\citation{swebok}
\citation{turing-way}
\citation{wpf}
\citation{humphrey}
\citation{managers}
\@writefile{toc}{\contentsline {subsection}{\numberline {8.b}SEBs are necessary but not sufficient}{39}{subsection.8.2}\protected@file@percent }
\@writefile{toc}{\contentsline {section}{\numberline {9}Software engineering best practice}{39}{section.9}\protected@file@percent }
\newlabel{supplement-best-practice}{{9}{39}{Software engineering best practice}{section.9}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.a}Requirements}{39}{subsection.9.1}\protected@file@percent }
\citation{differential-equations}
\citation{cbc}
\citation{spark}
\citation{misra}
\citation{hoare}
\citation{hoare}
\citation{numerals}
\citation{heedless}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.b}Formal methods}{40}{subsection.9.2}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.c}Defensive programming}{40}{subsection.9.3}\protected@file@percent }
\citation{onlyPaperWithChecks}
\citation{tweet,plos}
\citation{heedless}
\citation{spark}
\citation{haskell}
\citation{basic-reproducibilty,reproducibility}
\citation{NVP}
\citation{avianFluModel}
\citation{ICmodel}
\citation{flu-model}
\citation{excel1,excel2}
\citation{npm}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.d}Using inappropriate programming languages undermines reliability}{41}{subsection.9.4}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.e}Open source and version control}{41}{subsection.9.5}\protected@file@percent }
\citation{open-source}
\citation{sommerville,knight,NVP}
\citation{assurance-case}
\citation{LP}
\citation{relit}
\citation{hci1,hci2}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.f}Rigorous testing}{42}{subsection.9.6}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.g}Good documentation and record keeping}{42}{subsection.9.7}\protected@file@percent }
\citation{flexibility}
\citation{iso}
\citation{178C}
\citation{fixit}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.h}Usability}{43}{subsection.9.8}\protected@file@percent }
\newlabel{supplement-material-makefiles}{{9.h}{43}{Usability}{subsection.9.8}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.i}Reusing quality solutions}{43}{subsection.9.9}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.j}Simplicity}{43}{subsection.9.10}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.k}Compliance with standards}{43}{subsection.9.11}\protected@file@percent }
\citation{peerReview,knight}
\citation{ssi-report,ssi-url}
\citation{acm-artifacts}
\citation{security-engineering,cyber-cacm}
\citation{example-numerical-error}
\citation{hamming}
\citation{Schneier}
\citation{electronic-evidence}
\@writefile{toc}{\contentsline {subsection}{\numberline {9.l}Effective multidisciplinary teamwork}{44}{subsection.9.12}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.m}Continuous Professional Development (CPD)}{44}{subsection.9.13}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.n}Security and other factors}{44}{subsection.9.14}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {9.o}Software is a human activity}{44}{subsection.9.15}\protected@file@percent }
\citation{fixit}
\citation{popper-conjectures-refutations}
\citation{simon-artificial}
\citation{dunning-kruger,dunning-kruger-numeracy}
\citation{dunning-kruger}
\citation{fixit}
\citation{enigma}
\citation{harking}
\citation{viruses}
\@writefile{toc}{\contentsline {section}{\numberline {10}Code, data, and publication}{45}{section.10}\protected@file@percent }
\newlabel{supplement-on-code-data-publication}{{10}{45}{Code, data, and publication}{section.10}{}}
\citation{viruses}
\citation{strachey}
\@writefile{toc}{\contentsline {subsection}{\numberline {10.a}When magic numbers become magic code}{46}{subsection.10.1}\protected@file@percent }
\citation{henderson}
\citation{paper-usesRMarkdown}
\citation{RMarkdown}
\@writefile{toc}{\contentsline {subsection}{\numberline {10.b}When data is code}{47}{subsection.10.2}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {10.c}Exploiting code as data for more reliable science}{47}{subsection.10.3}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {10.d}When data is text: Exploiting code for reliable publication}{47}{subsection.10.4}\protected@file@percent }
\citation{Spiegelhalter}
\@writefile{toc}{\contentsline {subsection}{\numberline {10.e}Data and polynomials used in the paper}{48}{subsection.10.5}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {10.f}Comparing conventional and RAP approaches}{48}{subsection.10.6}\protected@file@percent }
\newlabel{supplement-RAP-diagrams}{{10.f}{48}{Comparing conventional and RAP approaches}{subsection.10.6}{}}
\@writefile{toc}{\contentsline {section}{\numberline {11}The Spiegelhalter trustworthiness questions}{48}{section.11}\protected@file@percent }
\newlabel{supplement-Spiegelhalter-section}{{11}{48}{The Spiegelhalter trustworthiness questions}{section.11}{}}
\@writefile{lof}{\contentsline {figure}{\numberline {2}{\ignorespaces The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}}{49}{figure.2}\protected@file@percent }
\newlabel{supplement-fig:basic}{{2}{49}{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code}{figure.2}{}}
\@writefile{lof}{\contentsline {figure}{\numberline {3}{\ignorespaces When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }}{49}{figure.3}\protected@file@percent }
\newlabel{supplement-fig:excel}{{3}{49}{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication}{figure.3}{}}
\@writefile{lof}{\contentsline {figure}{\numberline {4}{\ignorespaces Improving over the normal approach (figure \ref {supplement-fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX  \ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX  \ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}}{50}{figure.4}\protected@file@percent }
\newlabel{supplement-fig:rap}{{4}{50}{Improving over the normal approach (figure \ref {supplement-fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX \ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX \ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen}{figure.4}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {11.a}How trustworthy are the numbers?}{50}{subsection.11.1}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {5}{\ignorespaces In a notebook system, such as \emph  {Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation. Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}}{51}{figure.5}\protected@file@percent }
\newlabel{supplement-fig:notebook}{{5}{51}{In a notebook system, such as \emph {Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation. Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc)}{figure.5}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {11.b}How trustworthy is the source?}{51}{subsection.11.2}\protected@file@percent }
\citation{lancet-retracted}
\citation{science-lancet1,science-lancet2}
\citation{lancet-learning}
\@writefile{toc}{\contentsline {subsection}{\numberline {11.c}How trustworthy is the interpretation?}{52}{subsection.11.3}\protected@file@percent }
\@writefile{toc}{\contentsline {section}{\numberline {12}A pilot survey of computational science}{52}{section.12}\protected@file@percent }
\newlabel{supplement-survey-section}{{12}{52}{A pilot survey of computational science}{section.12}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {12.a}Selected journal case studies}{52}{subsection.12.1}\protected@file@percent }
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.a.1}\emph  {The Lancet\/}}{52}{subsubsection.12.1.1}\protected@file@percent }
\citation{jvs1}
\citation{jvs2,jvs3}
\citation{jvs1}
\citation{numerals}
\citation{fda}
\@writefile{lot}{\contentsline {table}{\numberline {6}{\ignorespaces Conforming to the RAP{\tt  +}\ methodology, the abbreviated summary above was generated automatically, by using \texttt  {make data}. A full list of \texttt  {make} options is generated by \texttt  {make} or \texttt  {make help} when run on the Unix command line. }}{53}{table.6}\protected@file@percent }
\newlabel{supplement-table:options}{{6}{53}{Conforming to the \RAPstar \ methodology, the abbreviated summary above was generated automatically, by using \texttt {make data}. A full list of \texttt {make} options is generated by \texttt {make} or \texttt {make help} when run on the Unix command line}{table.6}{}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.a.2}\emph  {Journal of Vascular Surgery}}{53}{subsubsection.12.1.2}\protected@file@percent }
\newlabel{supplement-vascular-surgery-note}{{12.a.2}{53}{\emph {Journal of Vascular Surgery}}{subsubsection.12.1.2}{}}
\citation{ICmodel}
\citation{ICmodel}
\citation{ICmodel}
\@writefile{lot}{\contentsline {table}{\numberline {7}{\ignorespaces Overview of the peer-reviewed paper sample. (Convenient copy of main paper's table \ref {table-overview}.)}}{54}{table.7}\protected@file@percent }
\newlabel{supplement-table-overview}{{7}{54}{Overview of the peer-reviewed paper sample. (Convenient copy of main paper's table \ref {table-overview}.)}{table.7}{}}
\@writefile{lot}{\contentsline {table}{\numberline {8}{\ignorespaces Summary of survey results. (Convenient copy of main paper's table \ref {table-summary}.)}}{54}{table.8}\protected@file@percent }
\newlabel{supplement-table-summary}{{8}{54}{Summary of survey results. (Convenient copy of main paper's table \ref {table-summary}.)}{table.8}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {12.b}Pilot paper sample}{54}{subsection.12.2}\protected@file@percent }
\citation{nature-review}
\@writefile{lot}{\contentsline {table}{\numberline {9}{\ignorespaces Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt  {covid-sim} \cite  {ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the Supplemental Material), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper. At the time of cloning and checking all repositories in May 2023, paper [182]\ still had nothing in its repository except a single file still saying ``\ldots  \ code coming soon\nobreakspace  {}\ldots  ,'' despite 47\ months having already elapsed since the paper had claimed the code could be accessed in its repository.}}{55}{table.9}\protected@file@percent }
\newlabel{supplement-table-repo-summary}{{9}{55}{Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt {covid-sim} \cite {ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the \supplement ), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper. At the time of cloning and checking all repositories in \clonewhen , paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname \ still had nothing in its repository except a single file still saying ``\ldots \ code coming soon~\ldots ,'' despite \the \pubdelayinmonths \ months having already elapsed since the paper had claimed the code could be accessed in its repository}{table.9}{}}
\citation{open-source}
\citation{stability}
\@writefile{toc}{\contentsline {subsection}{\numberline {12.c}Summary of results}{56}{subsection.12.3}\protected@file@percent }
\newlabel{supplement-summary-of-results}{{12.c}{56}{Summary of results}{subsection.12.3}{}}
\citation{RS-policy}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.c.1}Current code policies of sampled journals}{57}{subsubsection.12.3.1}\protected@file@percent }
\newlabel{supplement-journal-policies-section}{{12.c.1}{57}{Current code policies of sampled journals}{subsubsection.12.3.1}{}}
\citation{ref-1}
\citation{ref-2}
\citation{ref-3}
\citation{ref-4}
\citation{ref-5}
\citation{ref-6}
\citation{ref-7}
\citation{ref-8}
\citation{ref-9}
\citation{ref-10}
\citation{ref-11}
\citation{ref-12}
\citation{paper-usesRMarkdown}
\citation{ref-14}
\citation{onlyPaperWithChecks}
\citation{ref-16}
\citation{ref-17}
\citation{ethics-paper}
\citation{ref-19}
\citation{ref-20}
\citation{ref-21}
\citation{ref-22}
\citation{ref-23}
\citation{example-numerical-error}
\citation{ref-25}
\citation{ref-26}
\citation{ref-27}
\citation{ref-28}
\citation{ref-29}
\citation{ref-30}
\citation{ref-31}
\citation{ref-32}
\gdef \LT@i {\LT@entry 
    {2}{26.55563pt}\LT@entry 
    {1}{214.35622pt}\LT@entry 
    {1}{208.35622pt}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.c.2}Sample assessment and scoring}{58}{subsubsection.12.3.2}\protected@file@percent }
\citation{prisma}
\@writefile{toc}{\contentsline {subsection}{\numberline {12.d}Assessment criteria and methods}{60}{subsection.12.4}\protected@file@percent }
\newlabel{supplement-data-methods-subsection}{{12.d}{60}{Assessment criteria and methods}{subsection.12.4}{}}
\citation{fixit}
\citation{fixit}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.d.1}Detecting and defending against error}{62}{subsubsection.12.4.1}\protected@file@percent }
\newlabel{supplement-detecting-against-error}{{12.d.1}{62}{Detecting and defending against error}{subsubsection.12.4.1}{}}
\citation{excel-fiasco}
\citation{latex-calculus}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.d.2}Defending against system problems}{63}{subsubsection.12.4.2}\protected@file@percent }
\bibstyle{revisedCompJ}
\bibdata{appendix.bib}
\bibcite{vancouver}{{{130}{}{{}}{{}}}}
\bibcite{cosmos}{{{131}{}{{}}{{}}}}
\bibcite{ai-ethics}{{{132}{}{{}}{{}}}}
\bibcite{science-lancet1}{{{133}{}{{}}{{}}}}
\bibcite{science-lancet2}{{{134}{}{{}}{{}}}}
\bibcite{lancet-learning}{{{135}{}{{}}{{}}}}
\bibcite{jvs1}{{{136}{}{{}}{{}}}}
\bibcite{jvs2}{{{137}{}{{}}{{}}}}
\bibcite{jvs3}{{{138}{}{{}}{{}}}}
\bibcite{swebok}{{{139}{}{{}}{{}}}}
\bibcite{wpf}{{{140}{}{{}}{{}}}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.d.3}Problems of restrictive journal policies}{64}{subsubsection.12.4.3}\protected@file@percent }
\newlabel{supplement-restrictive-policies}{{12.d.3}{64}{Problems of restrictive journal policies}{subsubsection.12.4.3}{}}
\@writefile{toc}{\contentsline {section}{\numberline {13}Additional references for Supplemental Material}{64}{section.13}\protected@file@percent }
\bibcite{humphrey}{{{141}{}{{}}{{}}}}
\bibcite{managers}{{{142}{}{{}}{{}}}}
\bibcite{differential-equations}{{{143}{}{{}}{{}}}}
\bibcite{numerals}{{{144}{}{{}}{{}}}}
\bibcite{heedless}{{{145}{}{{}}{{}}}}
\bibcite{plos}{{{146}{}{{}}{{}}}}
\bibcite{excel1}{{{147}{}{{}}{{}}}}
\bibcite{excel2}{{{148}{}{{}}{{}}}}
\bibcite{npm}{{{149}{}{{}}{{}}}}
\bibcite{hci1}{{{150}{}{{}}{{}}}}
\bibcite{hci2}{{{151}{}{{}}{{}}}}
\bibcite{flexibility}{{{152}{}{{}}{{}}}}
\bibcite{iso}{{{153}{}{{}}{{}}}}
\bibcite{178C}{{{154}{}{{}}{{}}}}
\bibcite{peerReview}{{{155}{}{{}}{{}}}}
\bibcite{ssi-report}{{{156}{}{{}}{{}}}}
\bibcite{ssi-url}{{{157}{}{{}}{{}}}}
\bibcite{security-engineering}{{{158}{}{{}}{{}}}}
\bibcite{cyber-cacm}{{{159}{}{{}}{{}}}}
\bibcite{Schneier}{{{160}{}{{}}{{}}}}
\bibcite{electronic-evidence}{{{161}{}{{}}{{}}}}
\bibcite{simon-artificial}{{{162}{}{{}}{{}}}}
\bibcite{dunning-kruger}{{{163}{}{{}}{{}}}}
\bibcite{dunning-kruger-numeracy}{{{164}{}{{}}{{}}}}
\bibcite{enigma}{{{165}{}{{}}{{}}}}
\bibcite{harking}{{{166}{}{{}}{{}}}}
\bibcite{viruses}{{{167}{}{{}}{{}}}}
\bibcite{strachey}{{{168}{}{{}}{{}}}}
\bibcite{henderson}{{{169}{}{{}}{{}}}}
\bibcite{lancet-retracted}{{{170}{}{{}}{{}}}}
\bibcite{fda}{{{171}{}{{}}{{}}}}
\bibcite{stability}{{{172}{}{{}}{{}}}}
\bibcite{RS-policy}{{{173}{}{{}}{{}}}}
\bibcite{latex-calculus}{{{174}{}{{}}{{}}}}
\bibcite{ref-1}{{{175}{}{{}}{{}}}}
\bibcite{ref-2}{{{176}{}{{}}{{}}}}
\bibcite{ref-3}{{{177}{}{{}}{{}}}}
\bibcite{ref-4}{{{178}{}{{}}{{}}}}
\bibcite{ref-5}{{{179}{}{{}}{{}}}}
\bibcite{ref-6}{{{180}{}{{}}{{}}}}
\@writefile{toc}{\contentsline {section}{\numberline {14}References for surveyed papers}{66}{section.14}\protected@file@percent }
\bibcite{ref-7}{{{181}{}{{}}{{}}}}
\bibcite{ref-8}{{{182}{}{{}}{{}}}}
\bibcite{ref-9}{{{183}{}{{}}{{}}}}
\bibcite{ref-10}{{{184}{}{{}}{{}}}}
\bibcite{ref-11}{{{185}{}{{}}{{}}}}
\bibcite{ref-12}{{{186}{}{{}}{{}}}}
\bibcite{paper-usesRMarkdown}{{{187}{}{{}}{{}}}}
\bibcite{ref-14}{{{188}{}{{}}{{}}}}
\bibcite{onlyPaperWithChecks}{{{189}{}{{}}{{}}}}
\bibcite{ref-16}{{{190}{}{{}}{{}}}}
\bibcite{ref-17}{{{191}{}{{}}{{}}}}
\bibcite{ethics-paper}{{{192}{}{{}}{{}}}}
\bibcite{ref-19}{{{193}{}{{}}{{}}}}
\bibcite{ref-20}{{{194}{}{{}}{{}}}}
\bibcite{ref-21}{{{195}{}{{}}{{}}}}
\bibcite{ref-22}{{{196}{}{{}}{{}}}}
\bibcite{ref-23}{{{197}{}{{}}{{}}}}
\bibcite{example-numerical-error}{{{198}{}{{}}{{}}}}
\bibcite{ref-25}{{{199}{}{{}}{{}}}}
\bibcite{ref-26}{{{200}{}{{}}{{}}}}
\bibcite{ref-27}{{{201}{}{{}}{{}}}}
\bibcite{ref-28}{{{202}{}{{}}{{}}}}
\bibcite{ref-29}{{{203}{}{{}}{{}}}}
\bibcite{ref-30}{{{204}{}{{}}{{}}}}
\bibcite{ref-31}{{{205}{}{{}}{{}}}}
\bibcite{ref-32}{{{206}{}{{}}{{}}}}
\gdef \@abspage@last{34}

\makeatother
\documentclass[10pt,a4paper]{article}
\usepackage[text={6.5in,10in},centering]{geometry}    
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\usepackage{doi}
\usepackage{longtable}
\usepackage{color}
\usepackage{amsmath,amssymb}
\usepackage{fancyhdr}    
\usepackage{graphicx}
\PassOptionsToPackage{dvipdfmx}{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}

\def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
\def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}    
% expand macros.tex
% due to finding out that PDF doesn't work everywhere, here's where we define the image type we're using for imaged created by the Mathematica notebooks
\def\imageFileSuffix{jpg}

\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{cite}

\renewcommand\thesubsection{\thesection.\alph{subsection}}
\renewcommand\thesubsubsection{\thesection.\alph{subsection}.\arabic{subsubsection}}

\def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
\def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}

\makeatletter
    \def\do@url@hyp{\do/}
    \usepackage{moreverb}
\makeatother

\DeclareUrlCommand\doi{\def\UrlLeft{{\textrm{DOI}\ } }}
\DeclareUrlCommand\url{\def\UrlLeft{{\textrm{URL}\ } }}
\DeclareUrlCommand\midurl{\def\UrlLeft{}\allowbreak }

\renewcommand{\thefootnote}{\arabic{footnote}}

\def\mytitle{Improving science that uses code}
\def\supplement{Supplemental Material}

\def\citeeg#1{[e.g., \citenum{#1}]}

% calculate rounded percentages
\newcount \t
\newcount \tu
\def\pc#1#2{\t = #1%
\multiply \t by 100000%
\divide \t by #2% ?? 0 times percentage
\tu = \t
\divide \t by 1000% percentage, but no idea of remainder
\multiply \t by 1000% 1000 times percentage, with 00 as bottom digits
\advance \tu by -\t% bottom two digits
\divide \t by 1000\relax%
% round to nearest integer
% if ending in > .5 round up
% if ending in exactly .5 round towards nearest even number
\ifnum \tu > 500 % round up
	\advance \t by 1 
\else
	\ifnum \tu = 500 
		\ifodd \t % it's odd, so round up to even number 
			\advance \t by 1
		\else % leave rounded to even number 	
		\fi
	\fi
\fi
\the\t\%}

% code to make digits into blocks of 3 (as in 1000 -> 1 000)
\def\xBlockSep{\textcolor{red}{\hskip 0.3em :}\hskip 0.3em} % International Standards are to use a small space. UK typically uses a comma
% NOTE currently, the few decimal numbers (eg 0.000 5) use hskip explicitly, since defining \xBlockSep as a comma would definitely be wrong for decimals
\newcount\xdigitBlockn
\newcount\xdigitBlocktmp
\def\xdigitBlock#1{%
        \xdigitBlockn=#1\relax
        \ifnum \xdigitBlockn < 0
                $-$%
                \xdigitBlockn = -\xdigitBlockn
        \fi
        \let \xdigitBlockpptemp \empty
        \loop \ifnum \xdigitBlockn > 999
                \xdigitBlocktmp = \xdigitBlockn
                \divide \xdigitBlockn by 1000
                \xdigitBlocktmp = \numexpr \xdigitBlocktmp - 1000*\xdigitBlockn \relax
                \edef \xdigitBlockpptemp{\xBlockSep\ifnum \xdigitBlocktmp < 100  0\ifnum \xdigitBlocktmp < 10 0\fi\fi \the\xdigitBlocktmp \xdigitBlockpptemp}%
        \repeat
        \the\xdigitBlockn
        \xdigitBlockpptemp
}

\def\digitBlock#1{\hbox{\xdigitBlock{#1}}}

% simple macro to use a number register to pluralize (add an s) to words....
% \plural{\t}{fred} => \the\t\ freds if plural, or => one fred if singular
\def\plural#1#2{\ifnum #1=1 
	one #2%
\else
	\the#1\ #2s%
\fi}

% initialiseBibliography <title> <starting number> <introductory text>
\newcount \bibciten \bibciten=0
\def\initialiseBibliography#1#2#3{% title, starting citation number, an initial paragraph
	\global\def\refname{\arabic{section} #1}
    \global\def\unnumberedrefname{#1}
    \global\bibciten=#2
    \global\def\startBibliography{#3}
}

\def\bibskip{\vskip 1ex} % the gap between bib items generated by data.js

% read in any constants defined from the JSON or Git data
% expand generated/constants.tex
% Generated by programs/data.js
\def\journalBreakdown{\emph{Lancet Digital Health\/} ($N=6$), \emph{Nature Digital Medicine\/} ($N=12$) and \emph{Royal Society Open Science\/} ($N=14$)}
\def\tabularJournalBreakdown{&\hbox to 3em {\hfill 6}\hskip 1em \emph{Lancet Digital Health}\\&\hbox to 3em {\hfill 12}\hskip 1em \emph{Nature Digital Medicine}\\&\hbox to 3em {\hfill 14}\hskip 1em \emph{Royal Society Open Science}\\}
\global\newcount \dataN \global\dataN=32
\global\newcount \countAuthors \global\countAuthors=264
\global\newcount \countHasBreach \global\countHasBreach=11
\global\newcount \countHasPolicy \global\countHasPolicy=26
\global\newcount \countUsesVersionControlRepository \global\countUsesVersionControlRepository=10
\global\newcount \counthasDataRepository \global\counthasDataRepository=9
\global\newcount \countNoCodeInRepo \global\countNoCodeInRepo=1
\global\newcount \numberOfJournals \global\numberOfJournals=3
\global\newcount \countCodetested \global\countCodetested=0
\global\newcount \hasDevelopedRigorously \global\hasDevelopedRigorously=0
\global\newcount \countFields \global\countFields=36
\global\newcount \countCommentedOut \global\countCommentedOut=7
\global\newcount \countNotCommentedOut \global\countNotCommentedOut=2
\global\newcount \countMissingCode \global\countMissingCode=1
\global\def \averagePagesPerAuthor{1.2916666666666667}
% end expanding generated/constants.tex
% expand generated/metadata.tex
% shell script (make-metadata.sh) generated LaTeX variable values counting errors detected by data.js
\newcount \JSONerrorCount
\JSONerrorCount = 30
\newcount \dataVariableCount
\dataVariableCount = 63
% end expanding generated/metadata.tex
% expand generated/covidsimSummary.tex
% data calculated from the Ferguson covid-sim repo
\def \covidsimkLOC {25}
\def \covidsimfiles {229}
\def \covidsimdata{734 Mb}
% end expanding generated/covidsimSummary.tex
% expand generated/clone-date.tex
% date generated by running generated/allGitRepos.sh downloading Git repos
\def\clonedate {\ignorespaces 25 May 2023}
\def\cloneyear {2023}
\def\clonemonth {05}
% end expanding generated/clone-date.tex

\newcount \pubdelayinmonths
\pubdelayinmonths=\cloneyear
\advance \pubdelayinmonths by -2019 % submitted in 2019
\multiply \pubdelayinmonths by 12
\advance \pubdelayinmonths by -6 % submitted in June
\advance \pubdelayinmonths by \clonemonth

\def\monthname#1{\ifcase#1 \or 
January\or 
February\or 
March\or 
April\or 
May\or 
June\or 
July\or 
August\or 
September\or 
October\or 
November\or 
December\fi}

\def\numbertoname#1{\ifcase #1 zero\or one\or two\or three\or four\or five\or six\or seven\or eight\or nine\else #1\fi}
\def\Numbertoname#1{\ifcase #1 Zero\or One\or Two\or Three\or Four\or Five\or Six\or Seven\or Eight\or Nine\else #1\fi}

\def\clonewhen{\monthname{\clonemonth} \cloneyear}

\def\RAPstar{RAP{\tt +}}
\def\RAPstars{RAPs{\tt +}}
\def\RAPstarp#1{RAP{\tt +}#1}
\def\italicRAPstar{RAP{\tt +}}
% end expanding macros.tex

\makeatletter
      \renewcommand{\thefootnote}{\arabic{footnote}}
      % count the number of bibcite{name}{value} in paper.aux
      \let\oldbibcite=\bibcite
      \newcount\mainNumberOfReferences \mainNumberOfReferences=0
      \def\bibcite#1#2{\global\advance\mainNumberOfReferences by 1\oldbibcite{#1}{#2}}
      % expand paper.aux 
\relax 
\providecommand\hyper@newdestlabel[2]{}
\providecommand\HyperFirstAtBeginDocument{\AtBeginDocument}
\HyperFirstAtBeginDocument{\ifx\hyper@anchor\@undefined
\global\let\oldnewlabel\newlabel
\gdef\newlabel#1#2{\newlabelxx{#1}#2}
\gdef\newlabelxx#1#2#3#4#5#6{\oldnewlabel{#1}{{#2}{#3}}}
\AtEndDocument{\ifx\hyper@anchor\@undefined
\let\newlabel\oldnewlabel
\fi}
\fi}
\global\let\hyper@last\relax 
\gdef\HyperFirstAtBeginDocument#1{#1}
